---
title: "VisualR_2"
author: "F.J. Padt"
date: "Saturday, March 28, 2015"
output: word_document
---

```{r}
# it seems to work now
# added some comments from TurboToad


require(graphics)

M <- as.table(cbind(c(18, 28, 14), c(20, 51, 28), c(12, 25, 9))) 
dimnames(M) <- list( Husband = c("Tall", "Medium", "Short"), 
                     Wife    = c("Tall"," Medium", "Short"))

assocplot(M, col = c("green", "red"))

```


```{r}
# install.packages("vcd")

library(vcd)
assoc(M)
 
```

```{r Spline}
require(graphics)
# Clean and prepare the data 
r1 <- c(7.9 , 67.6, 28.3, 53.6) 
r2 <- c(4.4 , 54.5, 29.9, 57.6) 
r3 <- c(10.2, 50  , 27.7, 53.4) 
r4 <- c(2.5 , 35.3, 22.2, 47) 
r5 <- c(8.5 , 46.3, 32.2, 50) 

data <- as.table(rbind(r1, r2, r3, r4, r5)) 
dimnames(data) <- list( 
  Town = c(" Sheffield"," Warrington", "Dewsbury"," Leicester"," Gloucester"),
  Vaccinated = c(" Yes (< 10)"," No (< 10)", "Yes (> 10)"," No (> 10)")) 

#Step 3: Plot the chart 
spineplot(data)
spineplot(data, col = c("darkred", "orange", "darkgreen", "yellow1"))

#step4: Mosaic Plot
mosaicplot(data, color = 1:4)
mosaicplot(data, color = 1:4, las = 1)
 
```

## Quick reference R code

### Figure 5.1 Box plot of the effect of Vitamin C on tooth growth

Lewis, N.D. (2014-02-02). Visualizing Complex Data Using R (p. 25).  . Kindle Edition. 

```{r 5.1}
data(ToothGrowth) 
boxplot(len ~ dose, data = ToothGrowth, 
        boxwex = 0.25, at = 1: 3 - 0.2, 
        subset = supp == "VC", col = "red", 
        xlab   = "Vitamin C dose mg", ylab = "Tooth length", 
        xlim   = c(0.5, 3.5), ylim = c(0, 35), yaxs = "i") 

boxplot(len ~ dose, data = ToothGrowth, 
        add    = TRUE, boxwex = 0.25, at = 1:3 + 0.2, 
        subset = supp == "OJ", col = "cyan") 

legend(2, 9, 
       c("Ascorbic acid (VC)", "Orange Juice Group (OJ)"), 
       fill = c("red", "cyan"))

```

### Figure 5.2 2d contour plot of the effect of Vitamin C on tooth growth

Lewis, N.D. (2014-02-02). Visualizing Complex Data Using R (p. 26).  . Kindle Edition. 

```{r 5.2}
# install.packages("extracat")
# install.packages("reshape") 

require(reshape) 
require(extracat) 

data(ToothGrowth) 
boxplot2g(ToothGrowth$dose, ToothGrowth$len, ToothGrowth$sup)

```

### Figure 5.3 2d contour plot of Iris data

Lewis, N.D. (2014-02-02). Visualizing Complex Data Using R (p. 26).  . Kindle Edition. 
```{r 5.3}
# install.packages("extracat") 

require(extracat) 

boxplot2g(iris$Sepal.Length, iris$Sepal.Width, iris$Species)

```

### Figure 5.4 relationship between tips and total bill given group size 

Lewis, N.D. (2014-02-02). Visualizing Complex Data Using R (p. 26).  . Kindle Edition. 

```{r 5.4}
# install.packages("extracat")
# install.packages("reshape") 

require(extracat) 
require(reshape) 

data(tips) 
boxplot2g(tips$total_bill, tips$tip, tips$size)

```

### Figure 5‑5 relationship between tips and total bill given day of week

Lewis, N.D. (2014-02-02). Visualizing Complex Data Using R (pp. 26-27).  . Kindle Edition. 

```{r 5.5}
# install.packages("extracat")
# install.packages("reshape") 

require(extracat) 
require(reshape) 

data(tips) 
boxplot2g(tips$total_bill, tips$tip, tips$day)

```

